### 2018-08-01 paper/squad-overlay-design.tex
minor

To counter this possibility, we propose a fallback:
when the current state $X=x$ is new, we compute a naive probability $Pf_d$ that $d$ stays online, given only $d$'s previous state:

$$ Pf_d = \frac{\left| \left\{ X_i \in \mathcal{X}_{d\text{ online}}, X_{i+1} \in \mathcal{X}_{d\text{ online}} \right\}_{i \in \left[0, |S| - 1\right]} \right|}{\left| \left\{ X_i \in \mathcal{X}_{d\text{ online}} \right\}_{i \in \left[0, |S| - 1\right]} \right|} $$

$Pf_d$ is an estimator of $d$'s average probability of being online two turns in a row. It will also be used as a baseline in the evaluation.

>>>>

To counter this possibility, we propose a fallback:
when the current state $X=x$ is new, we compute a naive probability $P'_d$ that $d$ stays online, given only $d$'s previous state:

$$ P'_d = \frac{\left| \left\{ X_i \in \mathcal{X}_{d\text{ online}}, X_{i+1} \in \mathcal{X}_{d\text{ online}} \right\}_{i \in \left[0, |S| - 1\right]} \right|}{\left| \left\{ X_i \in \mathcal{X}_{d\text{ online}} \right\}_{i \in \left[0, |S| - 1\right]} \right|} $$

$P'd$ will be advertised in spite of $P_d$. It will also be used as a baseline in the evaluation.
